\documentclass[a4paper,12pt]{article}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[russian]{babel}  
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage[unicode, pdftex]{hyperref}
\usepackage{rotating}
\usepackage{tabularborder}
\title{Supplement materials}
\author{Mysin I.E.}
\date{}

\begin{document}
\maketitle

\section{Programm instruments}
We have used simulator Neuron runned from Python. We have used the code of the models described in the articles by Bezaire and Koutsouridis. Pyramidal and bistratifired neurons were taken from the Kusturidis and Poirazi models, the source code of the models was taken from the repository \url{https://github.com/ModelDBRepository/181967}. The remaining neurons are taken from model of the Bezaire  with co-authors, the source code for the neuron models is taken from \url{https://github.com/ModelDBRepository/187604}. The source code of our model is available at \url{https://github.com/ivanmysin/CA1\_rhythms\_model}. \par
We have used libraries to process the simulated signals: numpy, scipy, elephant (ССЫЛКИ). Graphs were plotted with Matplotlib (ССЫЛКИ). The code of processing is also avalible at \url{https://github.com/ivanmysin/CA1\_rhythms\_model}.

\section{Models of artifitial spike generators}
External inputs to the CA1 field are simulated with artifitial spike generators. Almost all neurons in hippocampal formation are modulated by rhythms, therefore we have used von Misses disribution to take phase modulated spike trains:
\begin{equation}
f(\phi) = \frac{exp(\kappa \cdot cos(\phi - \mu) )  }{2\pi \cdot I_0(\kappa) }
\end{equation}
where $I_0(\kappa)$ is the modified Bessel function of order 0. The parameters $\mu$ and $1/\kappa$  are analogous to the mean and variance in the normal distribution. Degree of neuron firing coupling to phase of thythm typicaly is described with parameter $R$ - ray length. Parameter $\kappa$ can be taken from $R$ by following equations: 
\begin{equation}
\begin{matrix}
\kappa & = & \left\{
	\begin{matrix}
	2 \cdot R + R^3 + 5/6 \cdot R^5 & \mbox{if } R < 0.53 \\
	-0.4 + 1.39 \cdot R + 0.43 / (1 - R) & \mbox{if } 0.53 \leq   R < 0.85  \\
	1 / (3\cdot R - 4\cdot R^2 + R^3) & \mbox{if } R \geq 0.85 \\
	\end{matrix} \right.
\end{matrix}
\end{equation}
Simple model of spike generator can be presented with equations:
\begin{equation}
\label{eq:spike_prob_phases}
p_{sp} = \int_\phi^{\phi + \Delta \phi} f(\phi) d \phi
\end{equation}
where $p_{sp}$ is probabilty of spike generation during $\Delta \phi$.from phases, we can go to the time with frequency ($\omega$)
\begin{equation}
\frac{d \phi}{dt} = 2 \pi \omega, \ \phi(t)=2\pi t \omega, \ d\phi=2 \pi \omega dt
\end{equation}
we can join these equations:
\begin{equation}
p_{sp} = S \cdot \int_t^{t + \Delta t} f(2\pi t \omega) 2 \pi \omega dt
\end{equation}
$S$ is normalization coefficient to get given spike rate. Each generator is characterizeted by prefered phase ($\mu$), frequency ($\omega$), ray length ($R=0$ is mean that there is no coupling to phase, $R=1$ is full coupling to phase $\mu$) and spike rate (regulated by $S$). We add also latency for generator model, it is period after spike generation with zero probability of new spike. We have used such model for inpus from medial septum and (LEC !!!!!). \par
Neurons of medial entorhynal cortex modulated by theta and gamma rhythms. We have simulated neuron of the MEC as grid cells. It means that they show slow periodic activity. It can be simulated as product of probabilities simple oscillators:  
\begin{equation}
p_{grid} = S \cdot p_{sp}(\omega_{\theta}, \mu_{\theta}, R_{\theta}) \cdot  p_{sp}(\omega_{\gamma}, \mu_{\gamma}, R_{\gamma}) \cdot  p_{sp}(\omega_{grid}, \mu_{grid}, R_{grid})
\end{equation}
All parameters are given below.
Input from the CA3 field is simulated with simple generators and with place cells. The CA3 neurons without place field activity are modulated only by theta rhythm. Place cells are modulated by theta and gamma rhythms, place field is simulated with gaussian:  
\begin{equation}
p_{grid} = S \cdot p_{sp}(\omega_{\theta}, \mu_{\theta}, R_{\theta}) \cdot  p_{sp}(\omega_{\gamma}, \mu_{\gamma}, R_{\gamma}) \cdot 
\frac{exp \Big( \frac{-(t - t_{place})^2}{2 \cdot r_{place}^2}  \Big)}{2 \pi r_{place}}  
\end{equation}
where $t_{place}$ and $r_{place}$ are the center and radius of the place field in time domain.



\section{Neurons models}
\subsection{General notes on neuron models}
All neurons were multicompartments. Potential of each compartment is: 
\begin{eqnarray}
\label{eq:comon_potential}
C\frac{dV}{dt}=-\sum{I_{tm}}-I_{syn} + I_{ext}
\end{eqnarray}
where C is capacity in $\mu F/ cm^2$, V is potetial in mV, t is time in ms, I is current in $\mu A/cm^2$. $I_{tm}$ are transmembrane currents, they are described in following sections, and tables with parameters are given in \ref{tables_of_neurons}. Common equation for transmemrane currents is
\begin{equation}
I_{tm}= g_{max}\cdot x_1^N\cdot x_2^M \cdot x_3^K \cdot (V-E)
\end{equation}
where $ g_{max}$ maximal coduntance in $mS/ cm^2$, $E$ is reversal potantial for this channel in $mV$. $x_1,\ x_2, \ x_3$ are gate variables. All compartments have leak current:
\begin{equation}
I_{L}= g_{L} \cdot (V - E_{L})
\end{equation}
$g_{L}$ and $E_{L}$ are given in tables \ref{tables_of_neurons}.

All gate variables were described with classical equation: 
\begin{equation}
\frac{dx}{dt} = \frac{x_{\infty}(V) - x}{\tau_x(V)}
\end{equation}
The equations for $x_{\infty}(V)$ and $\tau_x(V)$ are given in the corresponding sections in in explicit form or they can be given in form of functions  $\alpha(V)$ and $\beta(V)$
\begin{equation}
\tau_x(V) =  \frac{1}{\alpha(V) + \beta(V)} \ \ \ 
x_{\infty}(V) = \alpha(V) \cdot \tau_x(V)
\end{equation}
Numerical scheme:
\begin{equation}
x_{t + \Delta t} = x_t+\Big(1 - exp \Big(-\frac{\Delta t}{\tau_x} \Big) \Big)\cdot (x_{\infty}-x_t) 
\end{equation}
where $\Delta t = 0.1 ms$ is integration step.

There is the function \textit{Q(T)} in description of some currents, it is given by:
\begin{equation}
\label{eq:QT}
Q(T)= \frac{F}{ R \cdot T }
\end{equation}
where \textit{R = 8.315\ joule/deg}, \textit{F = 9.648} $\cdot 10^4 \ Coul$,
\textit{T} is the temperature in degrees Kelvin. In all simulations \textit{T=310 deg}.


$I_{syn}$ in equation (\ref{eq:comon_potential}) is sum of synaptic current, which deascibed in section \ref{synapse_models}. 

External current ($I_{ext}$) in equation (\ref{eq:comon_potential}) simulates noise and influence of very long currents:
\begin{equation}
I_{ext} = I_{ext, mean} + \eta \cdot \sigma_{ext}
\end{equation}
where $I_{ext, mean}$ is constant value,  $ \eta$ is random value from normal disribution with nean equals 0 and standart deviation equals 1, $\sigma_{ext}=0.005 \mu A/cm^2/\sqrt{ms}$ is std of noise. To simulate heterogeineously $I_{ext, mean}$ for each neuron is chosen from lognormal distribution, mean and std are given below. 

\subsection{CA1 Pyramidal cell}
Пирамидные нейроны описывались с помощью 15-ти компартментной модели. В модели принимались во внимание сома, базальные дендриты, проксимальная и дистальная часть апикального дендрита. \par
Уравнение баланса для соматического компартмента:
\begin{eqnarray}
C\frac{dV_s}{dt}=-I_L-I_{Na}-I_{kdr}-I_A-I_M-I_H-I_{sAHP}-I_{mAHP}-I_{CaL}- \nonumber \\ -I_{CaT}-I_{CaR}-I_{buff}-I_{syn} + I_{ext}
\end{eqnarray}

Уравнение баланса для аксона:
\begin{equation}
C\frac{dV_a}{dt}=-I_L-I_{Na}-I_{kdr}-I_M-I_{syn}
\end{equation}

Уравнение баланса для базальных дендритов и проксимальной части апикального дендрита:
\begin{eqnarray}
C\frac{dV_{rad,ori}}{dt} =-I_L-I_{Na}-I_{kdr}-I_A-I_M-I_H-I_{sAHP}-I_{mAHP}- \nonumber \\-I_{CaL}-I_{CaT}-I_{CaR}-I_{buff}-I_{syn}+I_{ext}
\end{eqnarray}
Уравнение баланса дистальной части апикального дендрита:
\begin{equation}
C\frac{dV_{LM}}{dt}=-I_L-I_{Na}-I_{kdr}-I_A-I_{syn}+I_{ext}
\end{equation}
where \textit{I\textsubscript{L}} is the leak current,  \textit{I\textsubscript{Na}} is the fast sodium current, \textit{I\textsubscript{kdr}} is the delayed rectifier potassium current, \textit{I\textsubscript{A}} is the A-type potassium current, \textit{I\textsubscript{M}}
is the M-typepotassium current, \textit{I\textsubscript{H}} is a hyperpolarizing H-type current,
\textit{I\textsubscript{CaL}}, \textit{I\textsubscript{CaT}} and
\textit{I\textsubscript{CaR}} are the L-, T- and R-type \textit{Ca\textsuperscript{2+}} currents, respectively,
\textit{I\textsubscript{sAHP}} and \textit{I\textsubscript{mAHP}} are
slow and medium Ca\textsuperscript{2+} activated K\textsuperscript{+} currents,\textit{ I\textsubscript{buff}}
is a calcium pump/buffering mechanism and \textit{I\textsubscript{syn}} is the synaptic current. \textit{ I\textsubscript{ext}} is the tonic current and noise. The
parameters for all ionic currents are listed in Table \ref{table:ca1_pyramidal_cell_parameters}. \par
The sodium current is described by:
\begin{equation}
I_{Na}= g_{max, Na}\cdot m^2\cdot h\cdot s\cdot (V-E_{Na})
\end{equation}
an variable \textit{s} is introduced to account for dendritic location‑dependent slow attenuation of the sodium current (Poirazzi et al., 2003a, b). Activation and inactivation kinetics for ${I_{Na}}$ are given by:

\begin{equation}
m_{\infty}=\frac {1}{1+exp(-\frac{V+40} {3})} , \ \ \tau_m=0.05 \ ms
\end{equation}

\begin{equation}
h_{\infty}=\frac {1}{1+exp(\frac{V+45}{3})},  \  \tau_h = 0.5 \ ms,
\end{equation}

\begin{equation}
s_{\infty}=\frac{1+Na_{att}\cdot exp(\frac{V+60}{2})}{1+exp(\frac{V+60}{2})}
\end{equation}


\begin{equation}
\tau_s=\frac{0.00333\cdot  exp(0.0024 \cdot (V+60)\cdot
		Q(T))}{1+exp(0.0012 \cdot (V+60)\cdot Q(T))}
\end{equation}

\textit{Na\textsubscript{att}} variable represents the degree of sodium current
attenuation and varies linearly from soma to distal trunk
\textit{Na\textsubscript{att}} $\in$~[0, 1]: 1 -maximum 0 - zero attenuation (Table \ref{table:ca1_pyramidal_cell_parameters}). The delayed rectifier current is given by:

\begin{equation}
I_{Kdr} = g_{Kdr} \cdot m^2 \cdot (V-E_K)
\end{equation}

\begin{equation}
m_{\infty}=\frac{1}{1+exp(-\frac{V+42}{2})}, \tau_m = 2.2 \ ms
\end{equation}

The sodium and delayed rectifier channel properties are slightly different in the soma, axis and dendritic arbor. To fit
experimental data regarding the backpropagation of spike trains, soma and axon compartments have a lower threshold for
Na\textsuperscript{+} spike initiation (-57 mV) than dendritic ones -50 mV. Thus, the $m_{\infty}$ and $h_{\infty}$
somatic/axonic HH channel kinetics as well as the time constants for both $I_{Na}^{sa}$ and $I_{Kdr}^{sa}$, are modified as follows. For the sodium

\begin{equation}
m_{\infty}^{sa}=\frac {1}{1+exp(-\frac{V+44}{3})} ,\ \ 
h_{\infty}^{sa}=\frac {1}{1+exp(\frac{V+49}{3.5})}
\end{equation}

while for the potassium delayed rectifier

\begin{equation}
m_{\infty}^{sa}=\frac {1}{1+exp(-\frac{V+46.3}{3})}
\end{equation}

The somatic time constant for somatic/axonic \textit{Na}\textit{\textsuperscript{+}}~channel activation is kept the
same $\tau$\textsubscript{m} = 0.05 ms while for inactivation is set to $\tau$\textsubscript{h}= 1 ms. The $\tau$-value for the delayed rectifier channel activation is set to $\tau_{m}= 3.5 ms$.
The fast inactivating A-type K\textsuperscript{+ }current is described by
\begin{equation}
I_A = g_{max, A} \cdot n \cdot l \cdot (V - E_K)
\end{equation}

\begin{equation}
n_{\infty} = \frac{\frac{-0.01(V+21.3)}{exp(-(V+21.3)/35)-1}}{\frac{-0.01(V+21.3)}{exp(-(V+21.3)/35)-1} + \frac{0.01(V+21.3)}{exp( (V+21.3)/35)-1} } \ \ \tau_n=0.2 \ ms
\end{equation}

\begin{equation}
l_{\infty} = \frac{\frac{-0.01(V+58)}{exp( (V+58)/8.2)-1}}{\frac{-0.01(V+58)}{exp( (V+58)/8.2)-1} + \frac{0.01(V+58)}{exp(-(V+58)/8.2)-1}}
\end{equation}

\begin{equation}
\begin{matrix}
\tau_l & =
& \left\{
\begin{matrix}
5+2.6(V+20)/10 & \mbox{if } V > 20 mV \\
5 & \mbox{otherwise }
\end{matrix} \right.
\end{matrix}
\end{equation}


The hyperpolarizing h-current is given by
\begin{equation}
I_H=g_{max, H} \cdot H \cdot (V-E_H)
\end{equation}

\begin{equation}
H_{\infty }=\frac {1}{1+exp((V-V_{half})/8)}  
\end{equation}

\begin{equation}
\tau_{H}=\frac{exp( 0.003364\cdot
	(V-V_{halft})}{0.05 \cdot q10^{(T-33)/10} \cdot
	(1+a_{H})}
\end{equation}


\begin{equation}
a_{H}=exp( 0.008316 \cdot (V-V_{halft}))
\end{equation}
where \textit{q10} =  0.4, \textit{V\textsubscript{halft}}
see in Table \ref{table:ca1_pyramidal_cell_parameters}.

The slowly activating voltage‑dependent potassium current, \textit{I}\textit{\textsubscript{M}},~is given by the
equations:


\begin{equation}
I_m=10^{-4}\cdot T_{adj}(T)\cdot g_m\cdot m\cdot
(V-E_K)
\end{equation}


\begin{equation}
\alpha_m =  \frac{10^{-3}\cdot(V+30)}{(1-exp(-(V+30)/9))T_{adj}(T)} 
\end{equation}
\begin{equation}
\beta_m = \frac{ -10^{-3}\cdot(V+30)}{(1-exp((V+30)/9))T_{adj}(T)}
\end{equation}
\begin{equation}
T_{adj}(T)=2.3^{(T - 287)/10}
\end{equation}


The slow after-hyperpolarizing current, is given by:
\begin{equation}
I_{sAHP}= g_{max, sAHP} \cdot m^3 \cdot (V-E_K)
\end{equation}

\begin{equation}
\frac{dm}{dt}=\frac{\frac{Cac}{(1+Cac)}-m}{\tau_m}
\end{equation}

\begin{equation}
\tau_m=max \Big(\frac {1}{0.003 \cdot (1+Cac)\cdot 3^{(\text{deg}C-22)/10}}, \ 0.5 \Big)
\end{equation}
where 
$Cac=(40 \cdot [Ca^{2+}]_{in})^2$.

The medium after-hyperpolarizing current, I\textsubscript{mAHP} (Moczydlowski and Latorre, 1983), is given by:

\begin{equation}
I_{mAHP}= g_{max, mAHP}\cdot m\cdot (V-E_K)
\end{equation}

\begin{equation}
\alpha_m(V)=\frac{0.48}{1+\frac{0.18}{[Ca^{2+}]_{in}}\cdot exp(-1.68\cdot V\cdot Q(T))}
\end{equation}

\begin{equation}
\beta_m(V)=\frac{0.28}{1+\frac{[Ca^{2+}]_{in}}{0.011\cdot exp(-2\cdot V\cdot Q(T))}}
\end{equation}

Q(T) see formula (\ref{eq:QT}). \par
The somatic high-voltage activated (HVA) L-type Ca\textsuperscript{2+} current is given by


\begin{equation}
I_{CaL}^s= g_{max, CaL}^s\cdot m\cdot \frac{0.001 \cdot ghk(V, [Ca^{2+}]_{in}, [Ca^{2+}]_{out}) }{0.001 + [Ca^{2+}]_{in}}
\end{equation}

\begin{equation}
\alpha_m(V)= \frac{-0.275 \cdot (V+27.01)}{exp(-(V+27.01)/3.8)-1}
\end{equation}

\begin{equation}
 \beta_m(V)= 4.7 \cdot exp(-(V+63.01)/17)
\end{equation}


whereas the dendritic L-type calcium channels have different kinetics: 


\begin{equation}
I_{CaL}^d= g_{max, CaL}^d \cdot m^3 \cdot h \cdot
(V-E_{Ca})
\end{equation}

\begin{equation}
m_{\infty}(V)=\frac {1}{1+exp(-(V+37))}
\end{equation}
\begin{equation}
h_{\infty}(V)=\frac {1}{1+exp( (V+41)/0.5)}
\end{equation}

Their time constants are equal to $\tau_m$ = 3.6\textit{ms} and $\tau_h$=29\textit{ms}. The low-voltage activated (LVA) T-type Ca\textsuperscript{2+} channel kinetics are given by:
\begin{equation}
I_{CaT} = g_{max, CaT}\cdot m^2\cdot h \cdot \frac{0.001 \cdot ghk(V,[Ca^{2+}]_{in},[Ca^{2+}]_{out})}{0.001+[Ca^{2+}]_{in} }
\end{equation}

\begin{eqnarray}
ghk(V,\ [Ca^{2+}]_{in},\ [Ca^{2+}]_{out}) = \nonumber \\
= -x\cdot (1 - [Ca^{2+}]_{out}/[Ca^{2+}]_{in} \cdot exp(V/x)) \cdot f(V/x)
\end{eqnarray}

\begin{equation}
x=\frac{0.0853\cdot T}{2}, \\
f(z) = \begin{cases} 1-\frac {z}{2}, & if \ |z|<10^{-4} \\ \frac z{e^z-1}, & \  otherwise \ \end{cases}
\end{equation}

\begin{equation}
\alpha_m(V)=-0.196\cdot \frac{(V-19.88)}{exp(-(V-19.88)/10)-1} 
\end{equation}

\begin{equation}
\beta_m(V) = 0.046\cdot exp(-(V/22.73))
\end{equation}

\begin{equation}
\alpha_h(V)= 0.00011\cdot exp(-(V+57)/19)
\end{equation}
\begin{equation}
\beta_h(V)=\frac {0.68}{exp(-(V-15)/10)+1}
\end{equation}
where $[Ca^{2+}]_{in}$ and $[Ca^{2+}]_{out}$ are the internal and external calcium concentrations. The HVA R-type Ca2+ current is described by:
\begin{equation}
I_{CaR} = g_{max, CaR}\cdot m^3\cdot h\cdot (V-E_{Ca})
\end{equation}

The difference between somatic and dendritic CaR currents lies in the $\alpha(V)$, $\beta(V)$ and $\tau$ ~parameter
values. For the somatic current, $\tau_m$ = 100\textit{ms} and
$\tau_h$ = 5\textit{ms} while for the dendritic current $\tau_m$ = 50\textit{ms} and $\tau_h$=5 \textit{ ms}. The $\alpha(V)$ and $\beta(V)$ equations for dendritic CaR channels are:


\begin{equation}
m_{\infty}(V)=\frac {1}{1+exp(-(V+48.5)/3)}
\end{equation}
\begin{equation}
h_{\infty}(V)=\frac {1}{1+exp(V+53)}
\end{equation}
while for the somatic CaR channels:
\begin{equation}
m_{\infty}(V)=\frac {1}{1+exp(-(V+60)/3)}
\end{equation}
\begin{equation}
h_{\infty}(V)=\frac {1}{1+exp(V+62)}
\end{equation}

Finally, a calcium pump/buffering mechanism is inserted at the cell body and along the apical and basal trunk. The
mechanism is taken from~(Destexhe, Mainen, \& Sejnowski, 1994). The factor for
$Ca^{2+}$ entry was changed from
\textit{f\textsubscript{e}} = 10,000~to \textit{f\textsubscript{e}} = 10,000/18~and the rate of calcium removal was made 7 times faster. The kinetic equations are given by:

\begin{equation}
Ca_{input flow} = \begin{cases} \frac{-f_e \cdot I_{Ca, sum} }{0.2 \cdot F}, & if \ Ca_{input flow} > 0  \\ 0, & \  otherwise \ \end{cases}
\end{equation}

\begin{equation}
\frac{d[Ca^{2+}]_{in}}{dt}=Ca_{input flow} +\frac{[Ca^{2+}]_{0}-[Ca^{2+}]_{in}}{\tau_{Ca}}
\end{equation}

$[Ca^{2+}]_{0} = 10^{-4} \ mM, \ \tau_{Ca} = 1400 \ ms$


\bigskip

\subsection{Bistratified cells}
Дендритные нейроны описывались с помомощью 13-ти компартметной модели. Балансовое уравнение для потенциала для всех компартментов:
\begin{eqnarray}
C\frac{dV}{dt}=-I_L-I_{Na}-I_{Kdr}-I_A-I_{CaL}-I_{CaN} - \nonumber \\ -I_{AHP}-I_C-I_{syn}+I_{ext}
\end{eqnarray}
where \textit{C} is the membrane capacitance, \textit{V} is the membrane potential, \textit{I\textsubscript{L}}
is the leak current, \textit{I\textsubscript{Na}} is the sodium current, \textit{I\textsubscript{Kdr}} is the fast delayed rectifier K\textsuperscript{+} current, \textit{I}\textit{\textsubscript{A}} is the A-type K\textsuperscript{+} current,\textit{I\textsubscript{CaL}}
is the L-type Ca\textsuperscript{2+} current, \textit{I}\textit{\textsubscript{CaN}} is the N-type
Ca\textsuperscript{2+} current, \textit{I}\textit{\textsubscript{AHP}} is the Ca\textsuperscript{2+}-dependent
K\textsuperscript{+} (SK) current, \textit{I}\textit{\textsubscript{C}} is the Ca\textsuperscript{2+} and
voltage-dependent K\textsuperscript{+} (BK) current and \textit{I}\textit{\textsubscript{syn}} is the synaptic current.
The conductance and reversal potential values of all ionic currents are listed in Table ... .
The sodium current and its kinetics are described by:
\begin{equation}
I_{Na}=g_{max, Na} \cdot m^3 \cdot h \cdot (V-E_{Na})
\end{equation}

\begin{equation}
\alpha_m(V)=\frac{-0.3\cdot(V-25)}{1-exp(-0.2\cdot(V-25))}, \ \  \beta_m(V)=\frac{0.3\cdot(V-53)}{1-exp(0.2\cdot(V-53))} \ 
\end{equation}

\begin{equation}
\alpha_h(V)=\frac{0.23}{exp((V-3)/20)}, \ \  \beta_h(V)=\frac{3.33}{1+exp(-0.1\cdot(V-55.5))}\ \ \ 
\end{equation}

The fast delayed rectifier potassium current, \textit{I\textsubscript{Kdr}} is given by:
\begin{equation}
I_{Kdr} = g_{max, Kdr} \cdot n^4 \cdot (V-E_K)
\end{equation}

\begin{equation}
\alpha_{n}=\frac{-0.07\cdot(V-47)}{1-exp((V-47)/-6)}, \ \  \beta_{n}=0.264\cdot exp((V-22)/4)
\end{equation}

The N-type calcium current, \textit{I}\textit{\textsubscript{CaN}}, is given by

\begin{equation}
I_{CaN}=g_{max, CaN} \cdot c^2 \cdot d \cdot (V-E_{Ca})
\end{equation}

\begin{equation}
\alpha_c(V)=\frac{0.19\cdot(19.88-V)}{ exp(0.1 \cdot(19.88-V))-1}, \  \beta_c(V)=0.046 \cdot exp(-V/20.73)
\end{equation}

\begin{equation}
\alpha_d=1.6\cdot10^{-4}\cdot exp(-V/48.4) , \  \beta_d=\frac 1{1+exp(0.1 \cdot (39-V))}
\end{equation}

The Ca\textsuperscript{2+}-dependent K\textsuperscript{+} (SK) current, \textit{I\textsubscript{AHP}}, is described by

\begin{equation}
I_{AHP} = g_{max, AHP} \cdot q^2 \cdot (V-E_K)
\end{equation}

\begin{equation}
\alpha_q(V)=\frac{0.00246}{exp((12\cdot log_{10}([Ca^{2+}]_{in})+28.48)/-4.5)}
\end{equation} 
\begin{equation}
\beta_q(V)=\frac{0.006}{exp((12\cdot log_{10}([Ca^{2+}]_{in})+60.4)/35)}
\end{equation}

\begin{equation}
\label{eq:CaDynamics}
\frac{d[Ca^{2+}]_{in}}{dt}=B\sum_{T, N, L}
I_{Ca}-\frac{[Ca^{2+}]_{in}-[Ca^{2+}]_0}{\tau_{Ca}}
\end{equation}

where
\begin{equation}
B = 5.2\cdot 10^{-6}/(A \cdot d)
\end{equation}
in units of mol/(C m\textsuperscript{3}) for a shell of
surface area \textit{A} and thickness \textit{d} (0.2 $\mu $m) and  $\tau_{Ca}=10$ ms was the calcium removal rate. [\textit{Ca\textsuperscript{2+}}]\textit{\textsubscript{0}} = 5 $\mu$M was the resting calcium concentration. 
The Ca\textsuperscript{2+} and voltage-dependent K\textsuperscript{+} (BK) current, \textit{I\textsubscript{c}}, is:
\begin{equation}
I_C=g_{max, c} \cdot o \cdot (V-E_K)
\end{equation}

\begin{equation}
\alpha_{o} = \frac{0.28 \cdot[Ca^{2+}]_{in}}{[Ca^{2+}]_{in} + 0.00048	\cdot exp(-1.68 \cdot F \cdot V / (R \cdot T)) }
\end{equation}
\begin{equation}
\beta_{o} = \frac{0.48}{1 + [Ca^{2+}]_{in} / (0.13 \cdot 10^{-6} \cdot exp(-2 \cdot F \cdot V/ (R \cdot T))) )}
\end{equation}

The A-type K\textsuperscript{+} current,
\textit{I}\textit{\textsubscript{A}}, is described by\ \ 
\begin{equation}
I_A=g_{max, A} \cdot a \cdot b  \cdot (V-E_K)
\end{equation}

\begin{equation}
\alpha_a=\frac{0.02\cdot (13.1-V)}{exp(\frac{13.1-V}{10})-1}, \ 
\beta_a=\frac{0.0175  \cdot(V-40.1)}{exp(\frac{V-40.1}{10})-1}
\end{equation}

\begin{equation}
\alpha_b = 0.0016 \cdot exp \Big(\frac{V + 13}{-18} \Big), \  \beta_b=\frac{0.05}{1+exp(\frac{10.1-V}{5})}
\end{equation}

The L-type Ca\textsuperscript{2+} current, \textit{I\textsubscript{CaL}}, is described by


\begin{equation}
I_{CaL}=g_{max, CaL}\cdot s_{\infty }^2\cdot V \cdot
\frac{1-\frac{exp(2 \cdot F \cdot V/ (k \cdot T)) \cdot [Ca^{2+}]_{in}}{[Ca^{2+}]_{0}}} {1-exp(2 \cdot F \cdot V/(k \cdot T))} 
\end{equation}


where \textit{g}\textit{\textsubscript{CaL}} is the maximal conductance, \textit{s}\textsf{\textit{\textsubscript{∞}}}
is the steady-state activation variable, \textit{F} is Faraday’s constant, \textit{T} is the temperature, \textit{k} is
Boltzmann’s constant, [\textit{Ca\textsuperscript{2+}}]\textit{\textsubscript{0}} \ is the equilibrium calcium concentration and [\textit{Ca\textsuperscript{2+}}]\textit{\textsubscript{in}} is
described in equation (\ref{eq:CaDynamics}). The activation variable, \textit{s\textsubscript{∞}}, is then


\begin{equation}
\alpha_s(V) = \frac{15.69\cdot(-V+81.5)}{exp(\frac{-V+81.5}{10})-1} , \ \  
\beta_s(V )= 0.29\cdot exp(-V/10.86)
\end{equation}


\subsection{PV basket cells}
PV basket cells were described with 17-compartment model, 1 - soma and 16 - dendrites. Balace equation for all compartments:
\begin{eqnarray}
C\frac{dV}{dt}=-I_L-I_{Na}-I_{Kdr}-I_{CaL}-I_{CaN}-I_{KCaB}- \nonumber \\ 
-I_{KCaS}-I_{KA} -I_{syn} + I_{ext}
\end{eqnarray}

Sodium current for spike generation is:
\begin{equation}
\label{eq:Nav}
I_{Na} = g_{max, Na} \cdot m^3 \cdot h \cdot (V - E_{Na})
\end{equation}
\begin{equation}
\alpha_m = \frac{-0.3 \cdot (V + 43)}{exp(-0.2\cdot(V+43)) - 1}
\end{equation}
\begin{equation}
\beta_m = \frac{0.3 \cdot (V + 15)}{exp(0.2\cdot(V+15)) - 1}
\end{equation}
\begin{equation}
\alpha_h = \frac{0.23}{exp(0.05\cdot(V+65))}
\end{equation}
\begin{equation}
\beta_h = \frac{3.33}{exp(-0.1\cdot(V+12.5)) + 1}
\end{equation}

Delayed rectification potassium current is
\begin{equation}
\label{eq:Kdrfast}
I_{Kdr} = g_{max, Kdr} \cdot n^4 \cdot (V - E_K)
\end{equation}
\begin{equation}
\alpha_n = \frac{-0.07 \cdot(V + 18)}{exp(\frac{V + 18}{-6}) - 1}
\end{equation}

\begin{equation}
\beta_n = 0.264 \cdot exp \Big( \frac{V + 43}{40} \Big)
\end{equation}

L-type of calcium current is: 
\begin{equation}
\label{eq:CavL}
I_{CaL} = g_{max, CaL} \cdot m^2 \cdot h \cdot ghk(V, [Ca_{2+}]_{in}, [Ca_{2+}]_{out} )
\end{equation}

\begin{equation}
h = \frac{0.001}{0.001 +[Ca^{2+}]_{in} }
\end{equation}

\begin{equation}
\alpha_{m} = \frac{15.69 \cdot (81.5-V)}{exp(0.1(81.5-V)) - 1}
\end{equation}

\begin{equation}
\beta_{m} = 0.29 \cdot exp \Big(\frac{-V}{10.86}\Big)
\end{equation}

\begin{equation}
ghk = -x \cdot \Big(1 - \Big(\frac{[Ca_{2+}]_{in}}{[Ca_{2+}]_{out}} \Big) \cdot exp \Big(\frac{V}{x}\Big) \Big) \frac{V}{x \cdot exp(V/x) -1 }
\end{equation}
where
\begin{equation}
x = 0.04259 \cdot T
\end{equation}
Calcium current N-type is given by following equation: 
\begin{equation}
\label{eq:CavN}
I_{CaN} = g_{max, CaN} \cdot c^2 \cdot d \cdot (V - E_{Ca})
\end{equation}

\begin{equation}
\alpha_{c} = \frac{-0.19 \cdot (V - 19.88)}{exp(0.1(V - 19.88)) - 1}
\end{equation}

\begin{equation}
\beta_{c} = 0.046 \cdot exp \Big(\frac{-V}{20.73}\Big)
\end{equation}

\begin{equation}
\alpha_{d} = 0.00016 \cdot exp \Big(\frac{-V}{48.4}\Big)
\end{equation}

\begin{equation}
\beta_{d} = \frac{1}{exp(0.1 \cdot (39 - V)) + 1}
\end{equation}


Calcium-dependent potassium current B:
\begin{equation}
I_{KCaB} = g_{max, KCaB} \cdot n \cdot (V - E_K)
\label{eq:KvCaB}
\end{equation}
\begin{equation}
\alpha_n = \frac{0.28 \cdot [Ca^{2+}]_{in} }{ [Ca^{2+}]_{in} + 0.00048 \cdot exp(\frac{-1.68 \cdot F \cdot V}{R \cdot T})  } 
\end{equation}
\begin{equation}
\beta_n = \frac{0.48}{1 + 130000 \cdot [Ca^{2+}]_{in} \cdot exp(\frac{2 \cdot F \cdot V}{R \cdot T})}
\end{equation}

Calcium-dependent potassium current S:
\begin{equation}
\label{eq:KvCaS}
I_{KCaS} = g_{max, KCaS} \cdot q^2 \cdot (V - E_K)
\end{equation}
\begin{equation}
\alpha_q = q_{10} \cdot 15 \cdot ([Ca^{2+}]_{in})^2 , \  \beta_q = q_{10} \cdot 0.00025
\end{equation}
\begin{equation}
q10 = 3^{0.1\cdot (T - 307) } 
\end{equation}

A-type of potassium current is:
\begin{equation}
\label{eq:KvA}
I_{KA} = g_{max, KA} \cdot n \cdot l \cdot (V - E_K)
\end{equation}
\begin{equation}
n_{\infty} = \frac{1}{1 + exp(-21 \cdot (V + 33.6)/T)}
\end{equation}
\begin{equation}
\tau_n = \frac{exp(-21 \cdot (V + 33.6)/T) }
{q_{10} \cdot 0.02 \cdot (1 + exp(-21 \cdot (V + 33.6)/T))}
\end{equation}

\begin{equation}
l_{\infty} = \frac{1}{1 + exp(46.41 \cdot  (V + 83)/T)}
\end{equation}

\begin{equation}
\tau_l = \frac{exp(46.41 \cdot  (V + 83)/T) }
{q_{10} \cdot 0.08 \cdot (1 + exp(46.41 \cdot  (V + 83)/T))}
\end{equation}

\begin{equation}
q10 = 3^{0.1\cdot (T - 303) } 
\end{equation}


\subsection{CCK basket cells}
Холецистокенин-содержащие корзинчатые нейроны так же как и парвальбумин-содержащие описывались моделью из 17 компартментов, 1 - тело и 16 компартментов дендриты. Потенциал всех компарментов описывался следующим уравнением:
\begin{eqnarray}
C\frac{dV}{dt}=-I_L-I_{Na}-I_{Kdr}-I_{CaL}-I_{CaN}-I_{HCN}-I_{KCaS}- \nonumber \\
-I_{KA}-I_{KCaB}-I_{KGroup}-I_{syn} + I_{ext}
\end{eqnarray}

Sodium current is:
\begin{equation}
\label{eq:Navcck}
I_{Na} = g_{max, Na} \cdot m^3 \cdot h \cdot s \cdot (V - E_{Na})
\end{equation}
\begin{equation}
\alpha_m = \frac{-0.5 \cdot (V + 42)}{exp(-0.2\cdot(V+42)) - 1}
\end{equation}
\begin{equation}
\beta_m = \frac{0.3 \cdot (V + 13)}{exp(0.2\cdot(V+13)) - 1}
\end{equation}
\begin{equation}
\alpha_h = \frac{0.6}{exp(0.05\cdot(V+65))}
\end{equation}
\begin{equation}
\beta_h = \frac{1.31}{exp(-0.1\cdot(V+12.5)) + 1}
\end{equation}
\begin{equation}
\alpha_s = \frac{0.003}{exp( \frac{V+45}{6})}
\end{equation}
\begin{equation}
\beta_s = \frac{0.005}{exp(-0.05\cdot(V+35))}
\end{equation}

H-current is:
\begin{equation}
\label{eq:HCN}
I_{H} = g_{max, H} \cdot H^2 \cdot (V - E_{H})
\end{equation}

\begin{equation}
\tau_{H} = \frac{1}{q_{10}} \cdot \Bigg(120 + \frac{129.5}{1 + exp(1.2 \ (V + 59.3))} \Bigg)
\end{equation}

\begin{equation}
H_{\infty} =  \frac{1}{1 + exp(0.1 \ (V + 91))}
\end{equation}

\begin{equation}
q10 = 3^{0.1\cdot (T - 307) } 
\end{equation}

Potassium current:
\begin{equation}
\label{eq:KvGroup}
I_{KGroup} = g_{max, KGroup} \cdot n \cdot (V - E_K)
\end{equation}
\begin{equation}
\alpha_n(V) = \frac{-0.0189324 \cdot (V - 4.18371) }{exp(-0.15562\cdot (V - 4.18371)) - 1}
\end{equation}

\begin{equation}
\beta_n(V) = 0.015857 \cdot exp \Big(\frac{-V}{25.4834}\Big)
\end{equation}


$ I_{Kdr}, I_{CaL}, I_{CaN},I_{KCaS}, I_{KCaB}, I_{KA}$ were same as PV basket cells and described equations (\ref{eq:Kdrfast}, \ref{eq:CavL}, \ref{eq:CavN}, \ref{eq:KvCaS}, \ref{eq:KvCaB}, \ref{eq:KvA}) respectivly.

\subsection{OLM cells}
OLM нейроны моделировались с помощью 4 компартментов - 1 тело, 1 аксон и 2 дендритных компартмента. Уравнение потенциала для тела нейрона:
\begin{eqnarray}
C\frac{dV_s}{dt} = -I_L - I_{Na} - I_{Kdr} - I_{H} - I_{KA}-
 \nonumber \\
-I_{syn} + I_{ext}
\end{eqnarray}
Уравнение для дендритов
\begin{eqnarray}
C\frac{dV_d}{dt} = -I_L - I_{Na} - I_{Kdr} - I_{KA}-
\nonumber \\
-I_{syn} + I_{ext}
\end{eqnarray}
Уравнение для аксона
\begin{eqnarray}
C\frac{dV_a}{dt} = -I_L - I_{Na} - I_{Kdr} - I_{syn}
\end{eqnarray}
Натриевые токи, калиевые токи выпрямления моделировались также как и у PV корзинчатых нейронов, уравнения (\ref{eq:Nav}) и (\ref{eq:Kdrfast}) соответственно.
H-каналы:
\begin{equation}
\label{eq:HCNolm}
I_{H} = g_{max, H} \cdot H \cdot (V - E_{H})
\end{equation}

\begin{equation}
H_{\infty} =  \frac{1}{1 + exp(0.98 \cdot(V + 84.1))}
\end{equation}

\begin{equation}
\tau_{H} = 100 + \frac{1}{exp(-(17.9+0.116\cdot V)) + exp(0.09 \cdot V-1.84)   }
\end{equation}

Калиевый ток A-типа:
\begin{equation}
\label{eq:KvAolm}
I_{KA} = g_{max, KA} \cdot a \cdot b \cdot (V - E_K)
\end{equation}
\begin{equation}
a_{\infty} = \frac{1}{1 + exp(\frac{V + 14}{-16.6})  } \ \ \tau_a = 5
\end{equation}
\begin{equation}
b_{\infty} = \frac{1}{1 + exp(\frac{V + 71}{7.3})  }
\end{equation}
\begin{equation}
\tau_b = \frac{1}{\frac{0.000009}{exp(\frac{V - 26}{18.5})}  + \frac{0.014}{exp(\frac{V +70}{-11}) + 0.2} }
\end{equation}


\subsection{Axo-axonic cells}
Аксо-аксональные интернейроны моделировались с помощью 17 компартментной модели: 1 сома и 16 компартментов для дендритов. Все компартменты описывались одинаковым набором каналов:
\begin{eqnarray}
C\frac{dV}{dt}=-I_L-I_{Na}-I_{Kdr}-I_{CaL}-I_{CaN}- \nonumber \\ 
-I_{KCaS}-I_{KA}-I_{KCaB}-I_{syn} + I_{ext}
\end{eqnarray}

Описание всех токов аналогично тем, что использовались выше для других нейронов, см. уравнения (\ref{eq:Nav}, \ref{eq:Kdrfast}, \ref{eq:CavL}, \ref{eq:CavN}, \ref{eq:KvCaS}, \ref{eq:KvA})

\subsection{Ivy and neurogiaform cells}
Ivy и нейроглиаформные описывались с помощью 17 компартментов: 1 сома и 16 дендритных компартментов. Все компартметны в обоих типах нейронов имели одинаковый набор каналов:
\begin{eqnarray}
C\frac{dV}{dt}=-I_L-I_{Na}-I_{Kdr} - I_{CaL}-I_{CaN}- \nonumber \\
-I_{KCaS} -I_{KA}-I_{KCaB}-I_{syn} + I_{ext}
\end{eqnarray}
Натриевые каналы:
\begin{equation}
\label{eq:Navngf}
I_{Na} = g_{max, Na} \cdot m^3 \cdot h \cdot (V - E_{Na})
\end{equation}
\begin{equation}
\alpha_m = \frac{-0.34133 \cdot (V + 24)}{exp(-0.2\cdot(V+24)) - 1}
\end{equation}
\begin{equation}
\beta_m = \frac{0.28483 \cdot (V -4)}{exp(0.2\cdot(V-4)) - 1}
\end{equation}
\begin{equation}
\alpha_h = \frac{0.29648}{exp(0.05\cdot(V+64.4184))}
\end{equation}
\begin{equation}
\beta_h = \frac{3.0931}{exp(-0.1\cdot(V+12.1463)) + 1}
\end{equation}

Калиевые каналы выпрямления:
\begin{equation}
\label{eq:Kdrfastngf}
I_{Kdr} = g_{max, Kdr} \cdot n^4 \cdot (V - E_K)
\end{equation}
\begin{equation}
\alpha_n = \frac{-0.07(V + 8)}{exp(\frac{V + 8}{-6}) - 1}
\end{equation}

\begin{equation}
\beta_n = 0.264 \cdot exp \Big( \frac{V + 33}{40} \Big)
\end{equation}

Калиевые токи А-типа:
\begin{equation}
I_{KA} = g_{max, KA} \cdot n \cdot l \cdot (V - E_K)
\end{equation}
\begin{equation}
n_{\infty} = \frac{1}{1 + exp(-34.8 \cdot (V + 23.6)/T)}
\end{equation}
\begin{equation}
\tau_n = \frac{exp(-34.8 \cdot (V + 23.6)) }
{0.02 \cdot q_{10} \cdot (1 + exp(-34.8 \cdot (V + 23.6)/T))}
\end{equation}

\begin{equation}
l_{\infty} = \frac{1}{1 + exp \cdot (46.41\cdot (V + 83)/T)}
\end{equation}

\begin{equation}
\tau_l = \frac{exp(46.41\cdot (V + 83)) }
{0.08 \cdot q_{10} \cdot (1 + exp(46.41\cdot (V + 83)/T))}
\end{equation}

\begin{equation}
q10 = 3^{0.1\cdot (T - 303) } 
\end{equation}

Описание всех остальных токов аналогично тем, что использовались выше для других нейронов, см. уравнения (\ref{eq:CavL}, \ref{eq:CavN}, \ref{eq:KvCaS}, \ref{eq:KvCaB})

\subsection{Schaffer collateral associated cells}
SCA cells описывались 17 компартмментами, 1 - сома и 16 дендриты. Все компарменты описывались с помощью следующего уравнения баланса:
\begin{eqnarray}
C\frac{dV_s}{dt}=-I_L-I_{Na}-I_{Kdr}-I_{CaL}-I_{CaN}-I_{H}-I_{KCaS}- \nonumber \\ -I_{KA}-I_{KCaB}-I_{KGroup}-I_{syn} + I_{ext}
\end{eqnarray}

Натриевый ток, $I_{KGroup}$ and $I_{H}$ описывались также как и для CCK basket cells - equation  (\ref{eq:Navcck}, \ref{eq:KvGroup}, \ref{eq:HCN}), уравнения для других каналов были аналогичны PV basket cells  (\ref{eq:CavL}, \ref{eq:CavN}, \ref{eq:KvCaS}, \ref{eq:KvA})

\subsection{Tables of neuronal parameters} \label{tables_of_neurons}
\input{pyrtable.tex}
\input{pvbastable.tex}
\input{aactable.tex}
\input{cckbastable.tex}
\input{olmtable.tex}
\input{ngftable.tex}
\input{ivytable.tex}
\input{scatable.tex}
\input{bistable.tex}

\section{Synapse models} 
\subsection{General description of synapse models} \label{synapse_models}
We simulate connections  via  gap junctions and chemichal synapses with AMPAR, NMDAR and GABA-A receptors. Model of gap junctions is described in  section (\ref{gap_junctions_models}).
Current trough all synaptic channels is simulated as:
\begin{equation}
I_{syn} = g_{max, syn} \cdot g \cdot (V - E_{syn})
\end{equation}
where $ g_{max, syn}$ is maximal synaptic conduntance in $mS/cm^2$, $g$ is analog of gate variable for synaptic current. $E_{syn}$ is reversal potential in $mV$, for excitatory synapses with AMPA and NMDA receptors $E_{syn} = 0\ mV$, for GABA-A channels $E_{GABA} = -75\ mV$.
Dynamic of $g$ is simulated with double exponetial model: 
\begin{equation}
\label{eq:gsyn}
g = exp \Big( \frac{t - t_0}{\tau_{rise}} \Big) - exp \Big( \frac{t - t_0}{\tau_{decay}} \Big)
\end{equation}
where $t_0$ is time of spike on presynaptic neuron with delay.
NMDAR simulated with equation:
\begin{equation}
I_{NMDA} = g_{max, NMDA} \cdot g \cdot s \cdot (V - E_{NMDA})
\end{equation}
\begin{equation}
s = \frac{1.50265}{1 + 0.33 \cdot exp(-0.0625 \cdot V) }
\end{equation}
where $g$ described by the same equation as AMPAR and GABA-A (\ref{eq:gsyn}).
Parameters $\tau_{rise},\ \tau_{decay}$ for synapses between each group of neurons are described in following sections. For each individual sinapses $g_{max, syn}$ and delay are chosen from lognormal distribution, mean and std are given below.  

\subsection{Synapses from pyramidal cells}
\input{aac_synapses.tex}
\input{bis_synapses.tex}
\input{cckbas_synapses.tex}
\input{ivy_synapses.tex}
\input{ngf_synapses.tex}
\input{olm_synapses.tex}
\input{pvbas_synapses.tex}
\input{pyr_synapses.tex}
\input{sca_synapses.tex}



\section{Gap junction models} \label{gap_junctions_models}
\subsection{General description of gap junction models}
Gap junction between two neurons (1 and 2) is described by simple equation:
\begin{equation}
I_{gap} = \frac{V_{1} - V_{2}}{R_{gap}}
\end{equation}
where $I_{gap}$ is current for neuron 1, $V_{1}$ and $V_{2}$ are potentials of neuron 1 and 2 respectivly. Gap junctions are always simmetrical, in equation of neuron 2 same current is added. $R_{gap}$ is resistance of contact, it is chosen randomly from normal disrtibuntion for each contact, parameters see below.


\subsection{Gap junctions between PV basket cells}

\subsection{Gap junctions between neurogliaform cells}



\section{Simulation of local field potetial} \label{field_potetial_model}
LFP simulated with LFPsim tools, we have used line aproximation:
\begin{equation} 
\Phi_{LFP} = \sum^{n}_{i=1}{ \frac{I_i}{2\pi \sigma}log \Big(\frac{\sqrt{h_i^2 + r_i^2}-h_i}{\sqrt{l_i^2 + r_i^2}-l_i} } \Big)
\end{equation}
$\Phi_{LFP}$ is simulated LFP, $I$ is transmemrane current.
In simulation of LFP only comratmments of pyramidal neurons were taken into account. $\sigma$ denotes
the conductivity of the medium. $r$ is the distance from
source to the point of measurement, $h$ is the distance from end of segment to point of measurement, $l$ is the length of secgment. All the pyramid neurons were arranged in an orderly fashion. The soma of all the cells were on the same level ($z=0$). The $x$ and $y$ coordinates for each neuron were chosen randomly from the circe with radius $R_{x, y}$ specified by the formula:
\begin{equation} 
R_{x, y} = \frac{\sqrt{\frac{N_{pyr}}{\rho_{pyr}} }} {\pi}
\end{equation}
where $N_{pyr}$ is the number of pyramidal cells in model, $\rho_{pyr} = 0.2 \ cell/\mu m^2$ is the dencity of cells in pyramidal layer of the CA1 field.
\end{document}



